Constructing the transition graphs of interacting hysterons

### 2022-06-14 Paper_draft.tex
Added numbers for permutations of switching fields

In practice, however, it is impractical to find the possible transition graphs by evaluating all possible orderings. This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs.\\

@@

We can thus distinguish three groups of $l=2$ graphs, as indicated in Fig. \ref{fig:N2l2}. The first group of graphs is realizable, and can therefore also be used as a base to construct $l=3$ graphs. For the second group, the graphs themselves are not realizable, but derived $l=3$ graphs may be realizable. For the third group, neither the $l=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable. To construct all possible $l=3$ graphs, we only need to use graphs from the first two groups.\\

>>>>

In practice, however, it is impractical to find the possible transition graphs by evaluating all possible orderings. This is because the transition graph only depends on a partial order of the switching fields, not on the total order, so that the number of permutations vastly outweighs the number of possible graphs. For example, for the interacting two-hysteron system, there are eight switching fields, giving $8! = 40320$ permutations, and for $N=3$ the number of permutations is $24! \approx 6\times 10^{23}$.\\

@@

We can thus distinguish three groups of $L=2$ graphs, as indicated in Fig. \ref{fig:N2l2}. The first group of graphs is realizable, and can therefore also be used as a base to construct $L=3$ graphs. For the second group, the graphs themselves are not realizable, but derived $L=3$ graphs may be realizable. For the third group, neither the $L=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable. To construct all possible $l=3$ graphs, we only need to use graphs from the first two groups.\\
